\chapter{Acknowledgment}

I want to dedicate this thesis to my loved ones. 

This work can not be completed without the guidance of Prof. Brendan O'Connor. Natural Language Processing is a new field for me but his faith on my ability makes everything easier. The learning opportunities that he offered me were invaluable. Thanks to him, I was able to meet other great researchers in the field, who left deep impressions on me. I admire him for always patiently listen to me and giving the best advice. I am lucky to have him as my advisor. 

I want to pay my respect to Prof. Erik Learned-Miller, who always takes good care of me during my four years of college. From the beginning, he appreciated my programming skills and guided me to my first research experience. He was a source of help whenever I ran into trouble. I will not forget your lessons about research and life, Professor!

I greatly appreciate the help of Caitlin Cellier. Discussing with her about errors in coreference resolution systems helped shaping my initial ideas for this work. 

I want to thank my awesome friends. I am fortunate to befriend with too many bright people. Their successful stories teach me that success comes from anywhere as long as you appreciate your opportunities. I wish them all the bests in their future careers.

My family is a part of me and always keep their eyes on my progress. I am thankful that I have awesome parents and a lovely sister. Just a few days ago, I still receive calls from them worrying about me not finishing this thesis. I hope this work would bring them happiness.

My sweetest words will be for my love, Huyen. When I am awake, she is asleep. When she sees the sun, I am already in my bed. But we still find time to encourage each other, and to practice generosity, tolerance and optimism together. We share the dream of being better people. Completing this thesis is my first attempt to fulfill that dream with her.     

Finally, thanks UMass for being a peaceful home for my four years of college. I didn't like the school at first but now I love it! I am and will always be proud to be a UMass student. 






