\documentclass[11pt,letterpaper]{article}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage[numbers]{natbib}      % http://merkel.zoneo.net/Latex/natbib.php
\usepackage{palatino}
\bibpunct{(}{)}{;}{a}{,}{,}
\usepackage{chngpage}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{subfigure}
\usepackage{parskip}
\usepackage[usenames,dvipsnames]{color}
\usepackage{indentfirst}
\definecolor{myblue}{rgb}{0,0.1,0.6}
\definecolor{mygreen}{rgb}{0,0.3,0.1}
\usepackage[colorlinks=true,linkcolor=black,citecolor=mygreen,urlcolor=myblue]{hyperref}
\newcommand{\bocomment}[1]{\textcolor{Bittersweet}{[#1 -BTO]}}
\newenvironment{itemizesquish}{\begin{list}{\labelitemi}{\setlength{\parskip}{0.6cm}\setlength{\itemsep}{0em}\setlength{\labelwidth}{2em}\setlength{\leftmargin}{\labelwidth}\addtolength{\leftmargin}{\labelsep}}}{\end{list}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\ignore}[1]{}

\newcommand{\solution}[1]{{\color{Blue}[\textbf{Solution:} #1]}}
\theoremstyle{definition}
\newtheorem{question}{Question}[section]
% \newtheorem{question}{Question}

\bibliographystyle{plainnat}
\setlength{\parindent}{30pt}
\linespread{1.5}

\title{
    Nonparametric regression 
}

\author{
	Khanh Nguyen
}

\date{March 12, 2015}

\begin{document}
\maketitle

We are given n pairs of observations ($x_1$, $y_1$), ..., ($x_n$, $y_n$), presumably drawn from the distribution $P(X, Y)$. We want to use those observations to estimate the regression function $r(x) = \mathbb E(Y \mid X = x)$ using weak assumptions on $r(x)$. The estimator of $r(x)$ is denoted by $\hat{r}_n(x)$.
\section{Linear Smoothers}
\textbf{Definition.} An estimator $\hat{r}_n$ is a \textbf{linear smoother} if, for each x, there exists a vector $l(x) = [l_1(x), ..., l_n(x)]$ such that:
$$\hat{r}_n(x) = \sum_{i = 1}^{n}l_i(x)y_i = l(x)^{\top}y$$

We gather all the vector $l(x_i)$ into a matrix $L$. Entry $(i, j)$ of $L$ is $l_j(x_i)$. 

\textit{Example.} Suppose that $a \leq x_i \leq b$, \textbf{regressogram} divides the interval (a, b) into m equally spaced bins denoted by $B_1, ..., B_m$. Then for $x \in B_j$:
$$\hat{r}_n(x) = \frac{1}{|B_j|} \sum_{i:x_i \in B_j}Y_i$$

\textit{Example.} Let $h > 0$ be a positive integer, called the bandwidth. The \textbf{Nadaraya-Watson} (NW) \textbf{kernel estimator} is defined by:
$$\hat{r}_n(x) = \sum_{i=1}^nl_i(x)y_i$$
where 
$$ l_i(x) = \frac{K(\frac{x - x_i}{h})}{\sum_{j = 1}^nK(\frac{x - x_i}{h})}$$

with $K$ being a kernel. 


For linear smoothers, there is always a hyper-parameter $h$ that controls that the degree of smoothness. To choose the optimal $h$, we conduct cross-validation, i.e. minimizing the cross-validation score $\hat{R}(h)$:
$$\hat{R}(h) = \frac{1}{n}\sum_{i=1}^n\left(\frac{y_i - \hat{r}_n(x_i)}{1 - L_{ii}}\right)^2$$


\section{Confidence interval}

The confidence interval for $\bar{r}_n = \mathbb{E}(\hat{r}_n(x))$ is 
$$\hat{r}_n(x) \pm c\hat{\sigma}(x)\norm{l(x)}$$

The constant $c$ is chosen as the $(1 - \alpha/2)$ quantile of the standard normal distribution, where $\alpha$ is the desired level of confidence.

To estimate the variance $\hat{\sigma}^2(x)$, we apply the following process recommended by \cite{wasserman2006all}:
\begin{enumerate}
\item Define $Z_i = \log(y_i - \hat{r}_n(x_i))^2$.
\item Regress the $Z_i$s on the $x_i$s (using nonparametric method) to get an estimate $\hat{q}_n(x)$ of $\log\sigma^2(x)$.
\item Set $\hat{\sigma}^2(x) = e^{\hat{q}_n(x)}$.
\end{enumerate}

\section{Local likelihood}

When $y$ is a binary variable, using local likelihood seems to be more appropriate. In this case, each $y_i$ is drawn from a Bernoulli distribution with parameter $r(x_i)$. We use the estimate:

$$\hat{r}_n(x) = \frac{e^{\hat{\theta_*}(x)}}{1 + e^{\hat{\theta_*}(x)}}$$

where $\hat{\theta_*}(x)$ maximizes the log-likelihood function:

$$l_x(\theta) = \sum_{i=1}^n K\left(\frac{x_i - x}{h}\right)\left(y_i\theta(x)^{\top}(x_i - x) - \log(1 + e^{\theta(x)^{\top}(x_i - x)})\right)$$

\bibliography{smoothing}

\end{document}






